---
title: "Integration with tidflowR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Integration with tidflowR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`tidplotR` is designed to pair naturally with `tidflowR` without requiring it.

The intended tandem workflow is:

1. `tidflowR` loads, validates, fetches, or aggregates data.
2. `tidplotR` turns the resulting data frames into reusable plots and SVG files.

## Example shape compatible with a tidflowR-style risk distribution

```{r}
library(tidplotR)

risk_categories <- data.frame(
  riskLevel = 1:4,
  label = c("low", "medium", "high", "critical"),
  colour = c("#53A63A", "#F9E49D", "#E88D21", "#AF2F2C"),
  stringsAsFactors = FALSE
)

palette <- stats::setNames(risk_categories$colour, risk_categories$label)

risk_df <- data.frame(
  indicator_id = rep("def01", 8),
  entity = rep(c("bedriften", "alle"), each = 4),
  riskLevel = rep(1:4, 2),
  andel_n = c(0.35, 0.33, 0.20, 0.12, 0.46, 0.24, 0.18, 0.12),
  stringsAsFactors = FALSE
)

plot_risk_comparison(
  risk_df,
  risk_categories = risk_categories,
  palette = palette
)
```

## Boundary guidance

- Keep data shaping and connector logic upstream in `tidflowR` or downstream
  consumer packages.
- Keep SVG writing and reusable plot builders here in `tidplotR`.
- Avoid introducing a hard package dependency in either direction unless the
  boundary is revisited explicitly.